SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper (minor): corrected a misprint and changed >= to \geq

    \path[draw,->]
    (1111.-45)
    .. controls +(7mm,-3mm) and +(3mm,-7mm) ..
    node[below right] {\begin{tabular}{@{}l@{}}
        tick\\
        {}[t1<Max1 \& t2<Max2]\\
        \{t1:=t1+1; t2:=t2+1\}
    \end{tabular}}
    (1111.-60)
    ;

    \path[draw,->]
    (1111) edge
    node[above right] {\begin{tabular}{@{}l@{}}
        ask\\
        {}[t1>=Max1 \& t2>=Max2]
    \end{tabular}}
    (2200)
    ;

@@

%% In Figure~\ref{schema:ArchFailure:BIP:Double} we show the combination
%% of two Failure Monitor architectures, with their respective controlled
%% processes.
In Figure~\ref{schema:ArchFailure:Double:OA} we show the open
automaton computed for the combined architecture of
Figure~\ref{schema:ArchFailure:BIP:Double}.
%
Comparing the guards of the transitions $\PortTick$ and $\PortAsk$
leaving state $1111$, we see that $\PortAsk$ can never be taken,
unless $\mathrm{Max1} = \mathrm{Max2}$.  This illustrates the
\emph{interference} phenomenon discussed in
\cite{AttieBBJS16-architectures-faoc}, showing that the liveness
property (\ref{eq:FM:liveness}) is not preserved when two copies of
the Failure Monitor architecture are composed together.\footnote{%
%
  One of the main results of \cite{AttieBBJS16-architectures-faoc}
  states that in a system obtained by an application of several
  architectures, liveness properties are preserved if these
  architectures are \emph{pair-wise non-interfering}.  However, no
  results were provided to check whether two are architectures are
  interfering or not.
%
} In this example, the interference is caused by the strong
synchronisation of the $\PortTick$ ports of the two architectures.  It
can be avoided by replacing the \mbox{$\PortTick
  \bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameTimer.\PortTick$} connector
in Figure~\ref{schema:ArchFailure:BIP} by \mbox{$\PortTick
  \blacktriangleright\!\!\!-\!\!\!-\!\!\!\bullet
  \NameTimer.\PortTick$} and applying the so-called \emph{maximal
  progress} whereby, whenever possible, the interaction $\{\PortTick,
\NameTimer.\PortTick\}$ is preferred to the firing of $\PortTick$
alone.  However, this fix goes beyond the scope of the current paper.

>>>>

    \path[draw,->]
    (1111.-45)
    .. controls +(7mm,-3mm) and +(3mm,-7mm) ..
    node[below right] {\begin{tabular}{@{}l@{}}
        tick\\
        {}[t1 < Max1 \& t2 < Max2]\\
        \{t1:=t1+1; t2:=t2+1\}
    \end{tabular}}
    (1111.-60)
    ;

    \path[draw,->]
    (1111) edge
    node[above right] {\begin{tabular}{@{}l@{}}
        ask\\
        {}[t1 $\geq$ Max1 \& t2 $\geq$ Max2]
    \end{tabular}}
    (2200)
    ;

@@

%% In Figure~\ref{schema:ArchFailure:BIP:Double} we show the combination
%% of two Failure Monitor architectures, with their respective controlled
%% processes.
In Figure~\ref{schema:ArchFailure:Double:OA} we show the open
automaton computed for the combined architecture of
Figure~\ref{schema:ArchFailure:BIP:Double}.
%
Comparing the guards of the transitions $\PortTick$ and $\PortAsk$
leaving state $1111$, we see that $\PortAsk$ can never be taken,
unless $\mathrm{Max1} = \mathrm{Max2}$.  This illustrates the
\emph{interference} phenomenon discussed in
\cite{AttieBBJS16-architectures-faoc}, showing that the liveness
property (\ref{eq:FM:liveness}) is not preserved when two copies of
the Failure Monitor architecture are composed together.\footnote{%
%
  One of the main results of \cite{AttieBBJS16-architectures-faoc}
  states that in a system obtained by an application of several
  architectures, liveness properties are preserved if these
  architectures are \emph{pair-wise non-interfering}.  However, no
  results were provided to check whether two architectures are
  interfering or not.
%
} In this example, the interference is caused by the strong
synchronisation of the $\PortTick$ ports of the two architectures.  It
can be avoided by replacing the \mbox{$\PortTick
  \bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameTimer.\PortTick$} connector
in Figure~\ref{schema:ArchFailure:BIP} by \mbox{$\PortTick
  \blacktriangleright\!\!\!-\!\!\!-\!\!\!\bullet
  \NameTimer.\PortTick$} and applying the so-called \emph{maximal
  progress} whereby, whenever possible, the interaction $\{\PortTick,
\NameTimer.\PortTick\}$ is preferred to the firing of $\PortTick$
alone.  However, this fix goes beyond the scope of the current paper.
